# RNeo4j

RNeo4j is Neo4j's R driver. It allows you to read and write data from / to Neo4j directly from your R environment.

## Contents

* [Install](#install)
* [Connect](#connect)
* [Nodes](#nodes)
* [Relationships](#relationships)
* [Cypher](#cypher)
* [Shortest Paths](#shortest-paths)
* [Weighted Shortest Paths](#weighted-shortest-paths)
* [Graph Algorithms](#graph-algorithms)
* [Visualizations](#visualizations)
* [Import](#import)

## <a name="#install"></a>Install

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("nicolewhite/RNeo4j")
library(RNeo4j)
```

```{r, echo=FALSE}
library(RNeo4j)
```

## <a name="#connect"></a>Connect

```{r}
graph = startGraph("http://localhost:7474/db/data/")
```

```{r, echo=FALSE}
clear(graph, input=F)
```

## <a name="#nodes"></a>Nodes

```{r}
nicole = createNode(graph, "Person", name="Nicole", age=24)
greta = createNode(graph, "Person", name="Greta", age=24)
kenny = createNode(graph, "Person", name="Kenny", age=27)
shannon = createNode(graph, "Person", name="Shannon", age=23)
```

## <a name="#relationships"></a>Relationships

```{r}
r1 = createRel(greta, "LIKES", nicole, weight=7)
r2 = createRel(nicole, "LIKES", kenny, weight=1)
r3 = createRel(kenny, "LIKES", shannon, weight=3)
r4 = createRel(nicole, "LIKES", shannon, weight=5)
```

## <a name="#cypher"></a>Cypher

If you're returning tabular results, use `cypher`, which will give you a `data.frame`.

```{r}
query = "
MATCH (nicole:Person)-[r:LIKES]->(p:Person)
WHERE nicole.name = 'Nicole'
RETURN nicole.name, r.weight, p.name
"

cypher(graph, query)
```

For anything more complicated, use `cypherToList`, which will give you a `list`.

```{r}
query = "
MATCH (nicole:Person)-[:LIKES]->(p:Person)
WHERE nicole.name = 'Nicole'
RETURN nicole, COLLECT(p.name) AS friends
"

cypherToList(graph, query)
```

## <a name="#shortest-paths"></a>Shortest Paths

```{r}
p = shortestPath(greta, "LIKES", shannon, max_depth=4)
n = nodes(p)
sapply(n, "[[", "name")
```

## <a name="#weighted-shortest-paths"></a>Weighted Shortest Paths

```{r}
p = shortestPath(greta, "LIKES", shannon, max_depth=4, cost_property="weight")
n = nodes(p)
sapply(n, "[[", "name")
p$weight
```

## <a name="#cypher"></a>Graph Algorithms

```{r, message=FALSE}
library(igraph)

query = "
MATCH (n)-->(m)
RETURN n.name, m.name
"

edgelist = cypher(graph, query)
ig = graph.data.frame(edgelist, directed=F)

betweenness(ig)
closeness(ig)
```

## <a name="#visualizations"></a>Visualizations

### `igraph`

```{r, message=FALSE}
plot(ig)
```

### `ggnet`

```{r, message=FALSE}
library(network)
library(GGally)

net = network(edgelist)
ggnet(net, label.nodes=TRUE)
```

### `visNetwork`

[Read this blog post](http://nicolewhite.github.io/2015/06/18/visualize-your-graph-with-rneo4j-and-visNetwork.html).

## <a name="#import"></a>Import

```{r, echo=FALSE}
clear(graph, input=F)
```

```{r}
library(hflights)
hflights = hflights[sample(nrow(hflights), 1000), ]

head(hflights)

addConstraint(graph, "Carrier", "name")
addConstraint(graph, "Airport", "name")

query = "
CREATE (flight:Flight {number: {FlightNum} })
SET flight.year = TOINT({Year}),
    flight.month = TOINT({DayofMonth}),
    flight.day = TOINT({DayOfWeek})

MERGE (carrier:Carrier {name: {UniqueCarrier} })
CREATE (flight)-[:OPERATED_BY]->(carrier)

MERGE (origin:Airport {name: {Origin} })
MERGE (dest:Airport {name: {Dest} })

CREATE (flight)-[o:ORIGIN]->(origin)
CREATE (flight)-[d:DESTINATION]->(dest)

SET o.delay = TOINT({DepDelay}),
    o.taxi_time = TOINT({TaxiOut})

SET d.delay = TOINT({ArrDelay}),
    d.taxi_time = TOINT({TaxiIn})
"

tx = newTransaction(graph)

for(i in 1:nrow(hflights)) {
  row = hflights[i, ]
  
  appendCypher(tx, query,
               FlightNum=row$FlightNum,
               Year=row$Year,
               DayofMonth=row$DayofMonth,
               DayOfWeek=row$DayOfWeek,
               UniqueCarrier=row$UniqueCarrier,
               Origin=row$Origin,
               Dest=row$Dest,
               DepDelay=row$DepDelay,
               TaxiOut=row$TaxiOut,
               ArrDelay=row$ArrDelay,
               TaxiIn=row$TaxiIn)
}

commit(tx)

summary(graph)
```